%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, letterpaper]{article}
\usepackage{fontspec}
%\usepackage{fontawesome}
\usepackage{listings}

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{letterpaper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}	
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
\setmonofont[Scale=1]{Inconsolata}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

\lstset{basicstyle=\ttfamily,breaklines=true}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Edward Greg Huang - vita},
	pdfauthor={Edward Greg huang},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

% DOCUMENT
\begin{document}
{\LARGE Edward Greg Huang}\\[1cm]
Office of the Secretary and Chief of Staff to the Regents \\
1111 Franklin Street, 12th Floor \\
Oakland, CA 94607-5200 \\
510.987.9220\\
Fax: 510.987.9224\\

% Department of Mathematics \\
% University of California at Berkeley \\
% Berkeley, CA 94704, USA \\[.2cm]

\href{mailto:eghuang@berkeley.edu}{\lstinline{eghuang@berkeley.edu}}\\
\href{https://www.eghuang.com}{www.eghuang.com}\\
\href{https://github.com/eghuang}{GitHub: eghuang}\\
\href{https://scholar.google.com/citations?user=DlUurWMAAAAJ}{Google Scholar}\\
%\vfill

%Born:  March 12, 1879---Ulm, Germany \\
Nationality: American

%%\hrule
\section*{Current position}
\emph{Undergraduate Student}, Department of Mathematics, University of California, Berkeley

%%\hrule
\section*{Areas of Interest}
 Algorithmic information theory • Deep learning • Biophysics 

%\hrule
\section*{Education}
\noindent
\years{2019}\textsc{B.A.} in Applied Mathematics, University of California, Berkeley\\
\years{2016}Study abroad, University of Hong Kong\\


%%\hrule
\section*{Academic Positions}
\noindent
\years{2018 - present}Student Advisor to the Regents, \textit{University of California} \\
\years{2018 - present}Artificial intelligence researcher, \textit{Intelligent Robotics Group, NASA Ames} \\
\years{2018}REU research fellow, \textit{Santa Fe Institute} \\
\years{2017 - present}Biophysics researcher, \textit{Lawrence Berkeley National Laboratory}\\ % \textit{NASA $ \& $ Department of Mathematics, UC Berkeley} \\
\years{2015 - 2017}Evolutionary ecology researcher, \textit{Department of Environmental Science, UC Berkeley}\\

%%\hrule
\section*{Industry $\&$ Nonprofit Experience}
\noindent
\years{2018}Senior Unit-Level Manager, \textit{Berkeley Student Cooperative} \\
\years{2017 - present}Brand Ambassador, \textit{Klättermusen AB} \\
\years{2017 - 2018}Vice President, \textit{Cal Hiking and Outdoor Society}\\
\years{2016}Financial Analyst Intern, \textit{EQS Group AG}\\
\years{2015 - 2016}Architectural Intern, \textit{Project M+}\\

\section*{Publications}

\subsection*{Journal articles}
\noindent
\years{2019}\textbf{Huang EG} (2019) Algorithmic information and inference devices. \emph{Manuscript in preparation}. \href{https://nbviewer.jupyter.org/github/eghuang/inferenceDevices/blob/master/inference_devices.pdf}{PDF} \\

\years{2019}\textbf{Huang EG}, Lin Y, Ebert M, Ham DW, Zhang CY, \& Sachs RK. (2019) Synergy theory for murine Harderian gland tumours after irradiation by mixtures of high-energy ionized atomic nuclei. \emph{Radiation and Environmental Biophysics}. \href{https://doi.org/10.1007/s00411-018-00774-x}{DOI}\\

\years{2018}Krehenwinkel H, Fong M, Kennedy S, \textbf{Huang EG}, Suzuki N, Cayetano L, \& Gillespie RG. (2018) The effect of DNA degradation bias in passive sampling devices on metabarcoding studies of arthropod communities and their associated microbiota. \emph{PLOS ONE 13(1): e0189188}. \href{https://doi.org/10.1371/journal.pone.0189188}{DOI} \\

\subsection*{Invited Talks $\&$ Presentations}
* indicates presenter\\


\noindent
\years{2019}\textbf{Huang EG}$^{*}$, Ham DW, Lin Y, Wang S, Zhao L, Zhang Y, Blakely EA, Chang PY $\&$ Sachs RK. (2019) Synergy theory: murine Harderian gland tumors and \textit{in vitro} chromosome aberrations induced by exposure to mixed beams with some high-LET components. Talk given at: \emph{2019 NASA Human Research Program Investigators' Workshop}; Jan 22 - 25; Galveston, Texas, USA. \href{https://nbviewer.jupyter.org/github/sachsURAP/NASA_HRP_2019/blob/master/hrp_abstract.pdf}{Abstract [PDF]} $ \& $ \href{https://nbviewer.jupyter.org/github/sachsURAP/NASA_HRP_2019/blob/master/hrp_slides.pdf}{Slides [PDF]} \\
\\

\years{2018}\textbf{Huang EG}$^{*}$, Wolpert DH. (2018) Connections between Turing machines and a formalization of knowledge. Talk given at: \emph{Santa Fe Institute REU Final Talks}; Aug 9; Santa Fe, New Mexico, USA. \href{https://www.youtube.com/watch?v=10bi_R47uYw&list=PLZlVBTf7N6GpTwEeQOlOmIfYN5J7zciZR&index=6&t=0s}{Video}\\

\years{2017}Ham DW, Gao J, Song BL, Yu J, Zhao LY, \textbf{Huang EG}$^{*}$, Lin Y, \& Sachs RK. (2017) Synergy theory in biology: Simulating radiation damage during interplanetary voyages as an example. Poster session presented at: \emph{11th Annual Biology and Mathematics in the Bay Area Conference; Nov 18}; San Francisco, California, USA. \href{https://nbviewer.jupyter.org/github/sachsURAP/BaMBA_11/blob/master/Bamba17v3.pdf}{PDF}\\

\subsection*{Book Chapters}
\noindent
\years{2015}Adhikari A, Ghosh DJ, \textbf{Huang EG}, et al. (2015) Theory Meets Data: A Data Scientist’s Handbook to Statistics. \emph{UC Berkeley Dept. of Statistics}. {\href{https://nbviewer.jupyter.org/github/eghuang/theory_meets_data/blob/master/theory-meets-data.pdf}{PDF}}\\

\subsection*{Authored software}
\noindent
\years{2017}\textbf{Huang EG}, Rominger AJ. (2017) \lstinline{kokua}: An \lstinline{R}-package of tools and data for Hawaiian ecology. \emph{\href{https://github.com/hawaiiDimensions/kokua}{GitHub}}\\

\years{2016}Rominger AJ, \textbf{Huang EG}. (2017) \lstinline{hdimDB}: Tools for biocollections database management in \lstinline{R}. \emph{\href{https://github.com/hawaiiDimensions/db/tree/master/hdimDB}{GitHub}}\\


%\hrule
\section*{Selected Programming Projects}
\noindent
\years{2018}\lstinline{deepFlood}: Deep learning framework to track floods using satellite imagery over TensorFlow.\\
\years{2018}\lstinline{abyss}: Rogue-like platform video game in Java.\\
\years{2018}\lstinline{BearMaps}: Web mapping service for the city of Berkeley in Java.\\
\years{2018}\lstinline{deque}: data structure implementation in Java.\\
\years{2017}\lstinline{simpleNeuralNet}: General feedforward neural network API in Python.\\
\years{2017}\lstinline{multiAgentSearch}: implementation of search algorithms in Python.\\
\years{2017}\lstinline{hdimGeo}: interactive map of biocollections data from the NSF Hawaii Dimensions project in \lstinline{R}. \\
\years{2017}\lstinline{kokua}: Open-source \lstinline{R}-package of tools and data for Hawaiian ecology.\\
\years{2017}\lstinline{hdimShiny}: Web application for ecological data wrangling.\\
\years{2016}\lstinline{hdimDB}: Open-source package of tools for biocollections database management in \lstinline{R}.\\
\years{2016}\lstinline{yelpMaps}: interactive map of Yelp data in Bay Area in Python.\\
\years{2016}\lstinline{schemeInterpreter}: Direct executor for Scheme programs in Python.\\

%\hrule
\section*{Grants, honors \& awards}
\noindent
\years{2018}REU Research Fellowship, National Science Foundation Grant No. 1757923 - \$7,000\\
\years{2017}Dean’s List, UC Berkeley\\
\years{2016}ASUC Student Opportunity Fund Grant, UC Berkeley - \$1,000\\
\years{2016}ASUC Academic Opportunity Fund Grant, UC Berkeley - \$250\\

%\hrule
%\section*{Service to the profession}


%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
%\fontspec{Times New Roman}
\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
\href{https://github.com/eghuang/cv/blob/master/cv.pdf}{Vitae on GitHub}}
\end{center}

\end{document}